Road Accident Prediction in Time and Space

### 2019-04-22 paper/paper.tex
Paper: progress on related work

\subsection{Related work}
Accident prediction has been extensively studied in the last decade. Historically, variation of the Poisson regression such as the negative binomial regression were used to predict the number of accident which occurred on a given road segment. The features usually used include feature from the road such as the number of lanes, the average daily traffic, and the curvature, and weather features such as average precipitation and the temperature. In 2005, Chang \cite{Change2005} compared the performances of a negative binomial regression with that of an Artificial Neural Network to predict the number of accident during a year on a road segment from a major freeway in Taiwan. The dataset used contains data from the years 1997 and 1998, which resulted in 1338 accidents. The ANN achieved slightly better result, with an accuracy of 61.4\% on the test dataset. On the same dataset, Chang et al.\cite{Chang2005b} also used decision trees for accident prediction in order to get more insight on the important variable for accident prediction. It appears that the average daily traffic and the number of days with precipitation are the most useful features. The decision tree reached an accuracy of 52.6\% on the test dataset. Lin et al. \cite{Lin2015} compared Frequent Pattern trees and random forests for feature selection and then k nearest neighbor and bayesian network for real-time accident prediction. Using the mean and sometimes the standard deviation of time series corresponding to the weather condition, the visibility, the traffic volume, the traffc speed and the occupancy, their models predict the occurence of an accident at the end of the time series. They obtain the best result using the Frequent Pattern trees feature selection and the  (add accuracy)
We note that the used a small sample of the possible negative examples.

  In addition, some other work aim at predicting the serverity of an accident using various information from the accident in order to understand what causes an accident to be fatal. Chong et al. \cite{Chong2005} used decision trees, neural network and an hybrid model using a decision tree and a neural network. They obtained thes best performances with the hybrid model which reached an accuracy of 90\% for the prediction of fatal injuries. They identified that the seatbelt usage, the light conditions and the alcohol usage of the driver are the most important features.

To be continued.
To cite: \cite{Theofilatos2017, Abellan2013, Lin2015}

Recently, the outstanding progress of deep learning algorithms has resulted in their extensive use in every field, including in Geospatial machine learning (Convolutional Neural Network and Long Short-Term Memory neural network for example) \cite{Yuan2018, QChen2016}.

>>>>

The rest of this paper is organized as follows: section 2 presents the related work of this paper, the section 3 presents the datasets we used and how we fused them to create positive and negative examples for the road accident prediction, the section 4 presents how we performed the feature engineering, the feature selection and the hyper-parameter tuning, the section 5 present our results and the section 6 discusses them.

\section{Related work}
Accident prediction has been extensively studied in the last decades. Historically, variation of the Poisson regression such as the negative binomial regression were used to predict the number of accident which occurred on a given road segment, but during the last decade machine learning algorithms have been use with success for accident prediction. The features usually used include feature from the road such as the number of lanes, the average daily traffic, and the curvature, as well as weather features such as average precipitation and the temperature. In 2005, Chang \cite{Change2005} compared the performances of a negative binomial regression with that of an Artificial Neural Network to predict the number of accident during a year on a road segment from a major freeway in Taiwan. The dataset used contains data from the years 1997 and 1998, which resulted in 1338 accidents. The ANN achieved slightly better result, with an accuracy of 61.4\% on the test dataset. On the same dataset, Chang et al.\cite{Chang2005b} also used decision trees for accident prediction in order to get more insight on the important variable for accident prediction. It appears that the average daily traffic and the number of days with precipitation are the most useful features. The decision tree reached an accuracy of 52.6\% on the test dataset. Lin et al. \cite{Lin2015} compared the performanced of Frequent Pattern trees with that of random forests for feature selection using then k nearest neighbor and bayesian network for real-time accident prediction. Using the mean and sometimes the standard deviation of time series corresponding to the weather condition, the visibility, the traffic volume, the traffc speed and the occupancy, their models predict the occurence of an accident at the end of the time series. They obtain the best result using the Frequent Pattern trees feature selection and achieved an accuracy of 61.7\%. We note that they used a small sample of the possible negative examples. Theofilatos\cite{Theofilatos2017} also used real-time data on two urban arterials of the city of Athens to study road accident likelihood and severity. Random Forests were used for feature selection and a Bayesian logistic regression for accident likelyhood prediction. The most important features identified were the coefficient of variation of the flow per lane, the speed and the occupancy, and the standard deviation of the speed and the occupancy.

  In addition, many publications aim at predicting the severity of an accident using various information from the accident in order to understand what causes an accident to be fatal. Chong et al. \cite{Chong2005} used decision trees, neural network and an hybrid model using a decision tree and a neural network. They obtained thes best performances with the hybrid model which reached an accuracy of 90\% for the prediction of fatal injuries. They identified that the seatbelt usage, the light conditions and the alcohol usage of the driver are the most important features. Abellán et al. \cite{Abellan2013} also studied traffic accident severity by looking at the decision rules of a decision tree using a dataset of 1801 highway accidents. They found that the the type and cause of the accident the light condition, the sex of the driver and the weather were the most important features.

All of these studies use relatively small datasets using data from only a few years or only a few roads. Indeed, it can be hard to collect all the necesssary informations to perform road accident prediction on a larger scale, and dealing with big dataset is more difficult. However, more recent studies performed accident prediction at a much larger scale, usually using deep learning models. Deep learning models can be trained online so that the whole dataset does not need to stay in memory. This makes it easier to deal with big datasets.

Chen et al. \cite{QChen2016} used human mobility information coming from mobile phone GPS data and historical accident records to build a model for real-time prediction of traffic accident risk in areas of 500 by 500 meters. The risk level of an area is defined as the sum of the severity of accidents that occured in the area during the hour. Their model achieves an RMSE of 1.0. They compared the performance of their deep learning model with the performances of some of the classical machine learning algorithms: a decision tree, a logistic regression and a Support Vector Machine (SVM), which all got worse performances of respectively 1.41, 1.41 and 1.73. We note that they have not tried the random forest algorithm which usually has good prediction performances. Najjar et al. \cite{Najjar2017}, trained a convolutional neural network using historical accident data and satelite images to predict the risk of accident on an intersection using the satellite image of the intersection. Their best model reach an accuracy of 73\%.

To cite: \cite{Ren2017, Yuan2018}.

\subsection{Related work on data imbalance ?}
